\chapter{Project Plan}
    This chapter will briefly talk about the 5S Drifter project motivations as well their function as a product developed 
    by the Minho's University  
\section{Introduction}
Under the course unity of Integrative Project in Industrial Electronics and Computers the students must
apply for professors projects in order to integrate unde their respective laboratories and start to undertand the pace
demanded on the Master's final paper.

This project is given by the professor Luis Gonçalves and Sergio Lopes unde the CMEMS laboratory
has the main porpouse to create a drifter for data aquisition. As a multi-themed project, this report will
explore multiple areas, as the PCB design for hardware and firmware manufacture, software design under the idea to optimize
the execution allowing for better performance. The main goal is to have the final product afloat at the end of the simester.
\subsection{Problem Statement}
The ocean is one of the man greatest mistery even before the written history. Humanity made the world ours over the water, 
from the Portuguese greatests discoveries, braving the raging ocean to the newst oil tanker demanding ever newer technology
in order to tame the sea for safer and smother sailing.

Nowadays cientists belive only 5\% of the ocean is discovered with the actual technology witch means that humanity 
know as much about our so grate sky as our own seas. 5S ocean drifter is a equipament made to acquire date from 
superficial sea streams and expand the oceangrapgh knowledge about it.

Better knowledge of the ocean lead to further development in diverse areas. Granting safety,
security and efficiency.

\subsubsection{Transport}
Sadly, ins't incommun to see transport accidents be reported and even worse for it to be a gigant
problem. Some of them are caused from the poor mapping of sea conditions. Tankers spiling oil, fishing vessels
getting capsized causing deaths. Even when there are no accidents, the poor knowledge from the tides lead to higher
consumes of energy once the route is setted against the streams.

A solution would be to create optimized shipping routes, minimizing accidents, and improving energy consumption
in order to traverse the waves.

A famous example of area to be carefull would be the Nazaré Canyon’s as their unic shape
create enormous waves.

\subsubsection{Ecology}

Fishing efficiency

Habitats

Renewable Energy 

\subsubsection{Oceanograpy}
Better undertanding of the Iberian Poleward Current (IPC)

\subsubsection{Geology}

Know where the sedimentation is leading to
\subsubsection{Sports}

\subsection{Problem Statement Analysis}

vila do conde + ou - 10km mar adentro 2g 4g\\

mapa de alcance na costa\\

atenção ao clima \\

latencia / sampling / tamanho do cartão sd\\ 
autonomia de NO MINIMO 5 DIAS \\
    consumo max 30mA \\
distancia da antena e da água \\
IMU caso tenha espaço para o consumo \\
SD memoria local \\
ADC a bateria \\
sensor de temperatura \\
database mongo db \\
